
# The Forssmann Situation

Response times for no go trials show a weird pattern. Usually, any response time > 1.5 s should be correct (reward), anything below should be incorrect (punishment).

```{r no_go}
data %>% 
  filter(condition == "no_go") %>% 
  
  ggplot(aes(x = feedback_type_rec, y = response_time_diff)) +
  geom_jitter(colour = "darkgreen", alpha = .3, size = 2) +
  geom_hline(aes(yintercept = 1.5), colour = "black", size = 1.5, linetype = "dashed") +
  scale_y_continuous(breaks = seq(0, 2, .25)) +
  labs(title = "No-go trials", subtitle = "punished vs. rewarded",
       y = "response time from go cue", x = "feedback") +
  my_theme
```

The same strange pattern occurs for no-go responses in go trials.

```{r go}
data %>% 
  filter(condition == "go") %>% 
  
  ggplot(aes(x = feedback_type_rec, y = response_time_diff, colour = response_rec)) +
  geom_jitter(alpha = .4, size = 2) +
  geom_hline(aes(yintercept = 1.5), colour = "black", size = 1.5, linetype = "dashed") +
  scale_y_continuous(breaks = seq(0, 2, .25)) +
  scale_colour_manual("response", values = c("lightblue3", "darkgrey", "darkred")) +
  labs(title = "Go trials", subtitle = "punished vs. rewarded",
       y = "response time from go cue", x = "feedback") +
  my_theme
```

We can find out where the two distinct populations of no-go response times are coming from by figuring out when which type (low is < 1.7 s; high is > 1.7 s) occurs when.

```{r weird_rts}
weird_RTs <- data %>% 
  filter(response_rec == "no go") %>% 
  mutate(response_time_split = ifelse(response_time_diff > 1.7, "high", "low"))
```

Turns out, no-go responses > 1.7 s are associated with one mouse, Forssmann.

```{r weird_rts_mouse}
weird_RTs %>% 
  group_by(response_time_split, mouse) %>%
  count() %>% 
  kable(col.names = c("response time", "mouse", "count")) %>% 
  kable_styling("striped")
```

The weird response times occur in sessions 4, 5, 6 and 7, which are all Forssmann's sessions.

```{r weird_rts_session}
weird_RTs %>% 
  group_by(response_time_split, session) %>%
  count() %>% 
  head() %>% # only show first 6 rows
  kable(col.names = c("response time", "session", "count")) %>% 
  kable_styling("striped")
```

Indeed, Forssmann is the culprit. We take him out from now on, since his timing will be messed up.

```{r no_go_forssmann}
data %>% 
  filter(condition == "no_go") %>% 
  mutate(Forssmann = ifelse(mouse == "Forssmann", "Forssmann", "other mice")) %>% 
  
  ggplot(aes(x = feedback_type_rec, y = response_time_diff, colour = Forssmann)) +
  geom_jitter(alpha = .4, size = 2) +
  geom_hline(aes(yintercept = 1.5), colour = "black", size = 1.5, linetype = "dashed") +
  scale_y_continuous(breaks = seq(0, 2, .25)) +
  scale_colour_manual("", values = c("darkred", "darkgreen")) +
  labs(title = "No-go trials", subtitle = "punished vs. rewarded",
       y = "response time from go cue", x = "feedback") +
  my_theme
```

```{r go_forssmann}
data %>% 
  filter(condition == "go") %>% 
  mutate(Forssmann = ifelse(mouse == "Forssmann", "Forssmann", "other mice")) %>% 
  
  ggplot(aes(x = feedback_type_rec, y = response_time_diff, colour = Forssmann,
             shape = response_rec2)) +
  geom_jitter(alpha = .4, size = 2) +
  geom_hline(aes(yintercept = 1.5), colour = "black", size = 1.5, linetype = "dashed") +
  scale_y_continuous(breaks = seq(0, 2, .25)) +
  scale_colour_manual("", values = c("darkred", "darkgreen")) +
  scale_shape_manual("", values = c(3, 16)) +
  labs(title = "Go trials", subtitle = "punished vs. rewarded",
       y = "response time from go cue", x = "feedback") +
  my_theme
```

```{r exclude_forssmann}
# data without Forssmann
data_wof <- data %>% 
  filter(mouse != "Forssmann")
```

```{r child = "02_behavioural_data_general.Rmd", echo = FALSE}
```
