
# The Lederberg Situation

Lederberg had a very different neural response from the others, and his behaviour is quote special as well. He seems to be consistently fast for correct responses. And doesn't seem to make any mistakes (except for no-go responses) at a contrast difference of one. In this section, we honour the smartest mouse in the experiment.

```{r lederberg_response_time}
data_wof %>% 
  filter(condition == "go") %>% 
  mutate(Lederberg = ifelse(mouse == "Lederberg", "Lederberg", "other mice")) %>% 
  
  ggplot(aes(x = factor(contrast_diff_abs), y = response_time_diff, colour = feedback_type_rec)) +
  geom_jitter(alpha = .4) +
  stat_summary(aes(fill = feedback_type_rec), size = 1, shape = 21, colour = "black") +
  theme(legend.position = "top") +
  facet_wrap(Lederberg~response_rec2) +
  scale_colour_manual("feedback", values = c("darkred", "lightblue3"), labels = c("wrong", "correct")) +
  scale_fill_manual("feedback", values = c("darkred", "lightblue3"), labels = c("wrong", "correct")) +
  labs(title = "Go trial response times", subtitle = "by correct response and contrast difference",
       y = "response time from go cue", x = "absolute contrast difference") +
  my_theme
```

We can also look at his performance (see a detailed description of the plot below). He makes less errors overall. If he makes errors, they are less likely to be no-go responses. He basically always goes for it :-) We may have excluded him, but we would like to honour the smartes mouse in the data set here.

```{r lb_response_type, out.width = '100%'}
# Have only the go trials.
# Recode the feedback type and the response type so we have one column that codes whether the mice made the correct
# choice, the wrong choice or a no-go response.
data_wof_go <- data_wof %>%
  filter(condition == "go") %>% 
  mutate(response_type = case_when(feedback_type_rec == "reward" ~ "correct",
                                   response_rec2 == "no go" ~ "no go",
                                   feedback_type_rec == "punishment" & response_rec2 == "other" ~ "wrong"),
         response_type = factor(response_type, levels = c("no go", "wrong", "correct")))
```

```{r lb_contrast_performance}
contrast_performance <- data_wof_go %>% 
  mutate(Lederberg = ifelse(mouse == "Lederberg", "Lederberg", "other mice")) %>% 
  
  group_by(Lederberg, response_type, contrast_diff_abs) %>% 
  count() %>% 
  # calculate percentage per contrast difference
  group_by(Lederberg, contrast_diff_abs) %>% 
  mutate(percentage = n/sum(n)) %>% 
  # transform into long format for plotting raw numbers and percentages as facets
  pivot_longer(cols = c(n, percentage), names_to = "type") %>% 
  mutate(type = ifelse(type == "n", "raw count", type))
```

```{r lb_contrast_performance_vis, out.width = '100%'}
contrast_performance %>% 
  
  ggplot(aes(x = factor(contrast_diff_abs), y = value, fill = response_type)) +
  geom_col() +
  scale_fill_manual("response", values = c("darkgrey", "darkred", "darkgreen")) +
  facet_wrap(Lederberg~type, scales = "free") +
  labs(title = "Performance", subtitle = "as a function of contrast difference",
       y = "", x = "absolute contrast difference") +
  my_theme
```

## References
